Study Level trends

### 2023-06-06 analysis/figures/06_study_change.Rmd
Save histogram figure

ses_wide_table %>% 
  count(rich_change, turnover, fun_change) 
```
```{r}
uncor_wide_table <-  wide_table %>%
  dplyr::select(-SES_FRic, -SES_FDiv, -SES_FEve) %>%
  mutate(rich_change = ifelse(!is.na(S), TRUE, FALSE),
         turnover = ifelse(!is.na(Jaccard_base), TRUE, FALSE),
         fun_change = case_when(
           if_all(c(FRic, FDiv, FEve), ~is.na(.)) ~ FALSE,
           .default = TRUE
         ))

@@

```{r, echo = FALSE, message = FALSE, fig.show = 'hold', fig.cap= "Break down of studies by the type of change they exhibited."}
plot_table <- duration_table %>%
  filter(group %in% c("A", "B", "C", "D"))

@@

library(kableExtra)

>>>>

ses_wide_table %>% 
  count(rich_change, turnover, fun_change) 
```

```{r}
uncor_wide_table <-  wide_table %>%
  dplyr::select(-SES_FRic, -SES_FDiv, -SES_FEve) %>%
  mutate(rich_change = ifelse(!is.na(S), TRUE, FALSE),
         turnover = ifelse(!is.na(Jaccard_base), TRUE, FALSE),
         fun_change = case_when(
           if_all(c(FRic, FDiv, FEve), ~is.na(.)) ~ FALSE,
           .default = TRUE
         ))

@@

```{r}
plot_table <- duration_table %>%
  filter(group %in% c("A", "B", "C", "D"))

@@

ggsave(here::here("figures/duration_hist.jpeg"), bg = "white")
```

```{r, echo = FALSE, message = FALSE, fig.show = 'hold', fig.cap= "Break down of studies by the type of change they exhibited."}
library(kableExtra)

knitr::include_graphics(here::here("figures/duration_hist.jpeg"))
